Severe Weather in the United States
========================================================
# Synopsis


Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to popuulation health?

Across the United States, which types of events have the greatest economic consequences?

Load libraries

```{r, echo = TRUE}

```

# Data Processing

Open data

```{r, echo = TRUE, cache=TRUE}
data = read.csv("repdata-data-StormData.csv")
```

head(data)


```{r, echo = TRUE}
head(data)
```

# Results
## Most harmful to population health

```{r, echo = TRUE}
fatality_sum = tapply(data$FATALITIES, data$EVTYPE, sum)
fat = data.frame(fatality_sum, names(fatality_sum))
injury_sum = tapply(data$INJURIES, data$EVTYPE, sum)
inj = data.frame(injury_sum, names(injury_sum))
occurrences = table(data$EVTYPE)
occ = data.frame(occurrences)
j = as.data.frame(cbind(occ$Freq,fat$fatality_sum, inj$injury_sum))
colnames(j) = c("Occurrences", "Fatalities", "Injuries")
j$fatality_per_occurrence = j$Fatalities / j$Occurrences
j$injuries_per_occurrence = j$Injuries / j$Occurrences

head(j[with(j, order(desc(j$injuries_per_occurence))),])
head(j[with(j, order(desc(j$fatality_per_occurence))),])
head(rev(sort(fatality_sum)))
head(rev(sort(injury_sum)))
head(rev(sort(occurrences)))
```

## Greatest economic consequences

```{r, echo = TRUE}

```








```{r, echo = TRUE}

```
